My title

### 2024-03-08 paper/paper.qmd
comment

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

>>>>

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults1
#| tbl-cap: "Explanatory models Political Preferences (n = 40000)"
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults2
#| tbl-cap: ""Explanatory models Political Preferences (n = 1000)"
#| warning: false
